---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages

```{r}
## helper
library(ggplot2)
library(dplyr)
library(tidyr)
library(stringr)
library(magrittr)
library(plyr)
library(mvtnorm)
library(Rlab)
library(plotrix)

## Load Matching for PS matching
library(Matching)
## Load FastDummies
library(fastDummies)
```

## Prepare data

```{r}
## Right heart cath dataset
rhc <- read.csv("http://biostat.mc.vanderbilt.edu/wiki/pub/Main/DataSets/rhc.csv")
## first 6 rows
head(rhc)
str(rhc)
with(rhc, unique(cat1))
## Show outcome (death) and exposure (swang1)
addmargins(table(rhc[,c("swang1", "death")]))
## Create weights for plotting
rhc$one <- 1
```

## Convert Categorical Variable to Dummies

```{r}
dmmy <- rhc %>% dplyr::select(cat1, cat2, ca, ninsclas, race, income) %>%
  dummy_cols(remove_first_dummy = TRUE) %>% 
  dplyr::rename("income_25_50k" = "income_$25-$50k", "income_11_25k" = "income_$11-$25k", "income_50k" = "income_> $50k")   %>%
  dplyr::select(-cat1, -cat2, -ca, -ninsclas, -race, -income) 
str(dmmy) 
colnames(dmmy) <- str_replace_all(names(dmmy), c(" " = "." , "," = ".", "/" = ".", "&" = "_"))
str(dmmy) 
```

## Combine RHC with dummy data frame

```{r}
RHC.D <- cbind(rhc, dmmy)
str(RHC.D)
```

## Construct propensity score model

```{r}
## PS model

psModel <- glm(swang1 ~ age + sex + edu + das2d3pc + dnr1 + surv2md1 + aps1 + scoma1 + wtkilo1 + temp1 + meanbp1 + resp1 + hrt1 + pafi1 + paco21 + ph1 + wblc1 + hema1 + sod1 + pot1 + crea1 + bili1 + alb1 + resp + card + neuro + gastr + renal + meta + hema + seps + trauma + ortho + cardiohx + chfhx + dementhx + psychhx + chrpulhx + renalhx + liverhx + gibledhx + malighx + immunhx + transhx + amihx +
 cat1_MOSF.w.Sepsis  +  cat1_MOSF.w.Malignancy  +   cat1_ARF  + cat1_CHF +  cat1_Coma +  cat1_Cirrhosis  + cat1_Lung.Cancer +   cat1_Colon.Cancer + cat2_MOSF.w.Sepsis + cat2_Coma + cat2_MOSF.w.Malignancy + cat2_Lung.Cancer + cat2_Cirrhosis + cat2_Colon.Cancer + ca_No + ca_Metastatic  + ninsclas_Private._.Medicare + ninsclas_Private  + ninsclas_Medicaid   + ninsclas_No.insurance + ninsclas_Medicare._.Medicaid + race_black + race_other  + income_25_50k + income_11_25k  + income_50k,
               family  = binomial(link = "logit"),
               data    = RHC.D)

length(psModel$coefficients)



##Create treatment assignment using ints
RHC.D$assign <- revalue(RHC.D$swang1, c("No RHC" = "0", "RHC" = "1"))
RHC.D$z <- as.numeric(as.character(RHC.D$assign))

#Making the outcome covariate into an integer
RHC.D$dth30 <- revalue(RHC.D$dth30, c("No" = "0", "Yes" = "1"))
RHC.D$dth30 <- as.integer(as.character(RHC.D$dth30))
                        
## PS (predicted probability of treatment)
RHC.D$ps <- predict(psModel, type = "response")
RHC.D$ATE <- 1
RHC.D$ATT <- RHC.D$ps
RHC.D$overlap <- RHC.D$ps*(1- RHC.D$ps)
str(RHC.D)
```


####Finding the Absolute Standardized Bias of all covariates using all estimation methods


#Reordering the data by treatment assignment

```{r}
z.order <- order(RHC.D$z)
z.order
RHC.D$z[z.order]

RHC.D0 <- RHC.D[z.order,]

n0 <- 3551
n1 <- 2184

```

#Creating dataframe only with covariates

```{r}

RHC.D01 <- RHC.D0[,-c(1:9, 27:28, 45, 48, 59:64)] #column 64 is all ones, maybe include?

#Making all factor covariates ints
RHC.D01$sex <- revalue(RHC.D01$sex, c("Female" = "0", "Male" = "1"))
RHC.D01$sex <- as.integer(as.character(RHC.D01$sex))

RHC.D01$dnr1 <- revalue(RHC.D01$dnr1, c("No" = "0", "Yes" = "1"))
RHC.D01$dnr1 <- as.integer(as.character(RHC.D01$dnr1))

RHC.D01$resp <- revalue(RHC.D01$resp, c("No" = "0", "Yes" = "1"))
RHC.D01$resp <- as.integer(as.character(RHC.D01$resp))

RHC.D01$card <- revalue(RHC.D01$card, c("No" = "0", "Yes" = "1"))
RHC.D01$card <- as.integer(as.character(RHC.D01$card))

RHC.D01$neuro <- revalue(RHC.D01$neuro, c("No" = "0", "Yes" = "1"))
RHC.D01$neuro <- as.integer(as.character(RHC.D01$neuro))

RHC.D01$gastr <- revalue(RHC.D01$gastr, c("No" = "0", "Yes" = "1"))
RHC.D01$gastr <- as.integer(as.character(RHC.D01$gastr))

RHC.D01$renal <- revalue(RHC.D01$renal, c("No" = "0", "Yes" = "1"))
RHC.D01$renal <- as.integer(as.character(RHC.D01$renal))

RHC.D01$meta <- revalue(RHC.D01$meta, c("No" = "0", "Yes" = "1"))
RHC.D01$meta <- as.integer(as.character(RHC.D01$meta))

RHC.D01$hema <- revalue(RHC.D01$hema, c("No" = "0", "Yes" = "1"))
RHC.D01$hema <- as.integer(as.character(RHC.D01$hema))

RHC.D01$seps <- revalue(RHC.D01$seps, c("No" = "0", "Yes" = "1"))
RHC.D01$seps <- as.integer(as.character(RHC.D01$seps))

RHC.D01$trauma <- revalue(RHC.D01$trauma, c("No" = "0", "Yes" = "1"))
RHC.D01$trauma <- as.integer(as.character(RHC.D01$trauma))

RHC.D01$ortho <- revalue(RHC.D01$ortho, c("No" = "0", "Yes" = "1"))
RHC.D01$ortho <- as.integer(as.character(RHC.D01$ortho))

```


#Finding the Absolute Standardized Bias (ASB) of all covariates using no weights

```{r}
RHC.D01$dem1.nw <- sum(RHC.D01$z)
RHC.D01$dem0.nw <- sum(1-RHC.D01$z)

N <- 71
noweights <- numeric(71)

for(i in 1:N){
  noweights[i] <- abs((sum(RHC.D01[,i]*RHC.D0$z)/RHC.D01$dem1.nw)[1] - (sum(RHC.D01[,i]*(1-RHC.D01$z))/RHC.D01$dem0.nw))[1] / (sqrt((var(RHC.D01[1:3551,i])/n0)+(var(RHC.D01[3552:5735,i])/n1)))
}

noweights
boxplot(noweights)

```

#Finding the Absolute Standardized Bias (ASB) of all covariates using ATE weights

```{r}
RHC.D01$omega1.ate <- 1/RHC.D01$ps
RHC.D01$omega0.ate <- 1/(1-RHC.D01$ps)
RHC.D01$dem1.ate <- sum(RHC.D01$z*RHC.D01$omega1.ate)
RHC.D01$dem0.ate <- sum((1-RHC.D01$z)*RHC.D01$omega0.ate)

N <- 71
ate <- numeric(71)

for(i in 1:N){
  ate[i] <- abs((sum(RHC.D01[,i]*RHC.D0$z*RHC.D01$omega1.ate)/RHC.D01$dem1.ate)[1] - (sum(RHC.D01[,i]*(1-RHC.D01$z)*RHC.D01$omega0.ate)/RHC.D01$dem0.ate))[1] / (sqrt((var(RHC.D01[1:3551,i])/n0)+(var(RHC.D01[3552:5735,i])/n1)))
}

ate
boxplot(ate)
```


#Finding the Absolute Standardized Bias (ASB) of all covariates using ATT weights

```{r}
RHC.D01$omega1.att <- 1
RHC.D01$omega0.att <- RHC.D01$ps/(1-RHC.D01$ps)
RHC.D01$dem1.att <- sum(RHC.D01$z*RHC.D01$omega1.att)
RHC.D01$dem0.att <- sum((1-RHC.D01$z)*RHC.D01$omega0.att)

N <- 71
att <- numeric(71)

for(i in 1:N){
  att[i] <- abs((sum(RHC.D01[,i]*RHC.D0$z*RHC.D01$omega1.att)/RHC.D01$dem1.att)[1] - (sum(RHC.D01[,i]*(1-RHC.D01$z)*RHC.D01$omega0.att)/RHC.D01$dem0.att))[1] / (sqrt((var(RHC.D01[1:3551,i])/n0)+(var(RHC.D01[3552:5735,i])/n1)))
}

att
boxplot(att)
```


#Finding the Absolute Standardized Bias (ASB) of all covariates using overlap weights

```{r}
RHC.D01$omega1.ol <- (1-RHC.D01$ps)
RHC.D01$omega0.ol <- RHC.D01$ps
RHC.D01$dem1.ol <- sum(RHC.D01$z*RHC.D01$omega1.ol)
RHC.D01$dem0.ol <- sum((1-RHC.D01$z)*RHC.D01$omega0.ol)

N <- 71
overlap <- numeric(71)

for(i in 1:N){
  overlap[i] <- abs((sum(RHC.D01[,i]*RHC.D0$z*RHC.D01$omega1.ol)/RHC.D01$dem1.ol)[1] - (sum(RHC.D01[,i]*(1-RHC.D01$z)*RHC.D01$omega0.ol)/RHC.D01$dem0.ol))[1] / (sqrt((var(RHC.D01[1:3551,i])/n0)+(var(RHC.D01[3552:5735,i])/n1)))
}

overlap
boxplot(overlap)
```

#Combining the 4 boxplots into 1 plot
```{r}
boxplot(noweights, ate, att, overlap, main="ASB for Covariates using RHC Study", 
        ylab = "Absolute Standardized Bias", xlab = "Weight Type")
axis(1, 1:4, c("Unweighted", "ATE", "ATT", "Overlap"))
```


####Finding the WATE of all estimation methods

#Turning the outcome covariate into an integer

```{r}
RHC.D0$dth30 <- revalue(RHC.D0$dth30, c("No" = "0", "Yes" = "1"))
RHC.D0$dth30 <- as.integer(as.character(RHC.D0$dth30))
```

#Truncating extreme propensity score values
```{r}
RHC.D.trunc <- RHC.D
ps.order.trunc <- order(RHC.D.trunc$ps)
ps.order.trunc
RHC.D.trunc$ps[ps.order.trunc]

RHC.D0.trunc <- RHC.D.trunc[ps.order.trunc,]

max <- max(which(RHC.D0.trunc$ps < 0.1))
min <- min(which(RHC.D0.trunc$ps > 0.9))

RHC.D0.trunc <- RHC.D0.trunc[-c(min:5735),]
RHC.D0.trunc <- RHC.D0.trunc[-c(1:max),]
```


#WATE using no weights

```{r}
RHC.D0$dem1.nw <- sum(RHC.D0$z)
RHC.D0$dem0.nw <- sum(1-RHC.D0$z)

((sum(RHC.D0$dth30*RHC.D0$z)/RHC.D0$dem1.nw)[1] - (sum(RHC.D0$dth30*(1-RHC.D0$z))/RHC.D0$dem0.nw)[1])
```

#WATE using ATE weights

```{r}
RHC.D0$omega1.ate <- 1/RHC.D0$ps
RHC.D0$omega0.ate <- 1/(1-RHC.D0$ps)
RHC.D0$dem1.ate <- sum(RHC.D0$z*RHC.D0$omega1.ate)
RHC.D0$dem0.ate <- sum((1-RHC.D0$z)*RHC.D0$omega0.ate)

(sum(RHC.D0$dth30*RHC.D0$z*RHC.D0$omega1.ate)/RHC.D0$dem1.ate)[1] - (sum(RHC.D0$dth30*(1-RHC.D0$z)*(RHC.D0$omega0.ate)/RHC.D0$dem0.ate)[1])
```

#WATE using ATT weights

```{r}
RHC.D0$omega1.att <- 1
RHC.D0$omega0.att <- RHC.D0$ps/(1-RHC.D0$ps)
RHC.D0$dem1.att <- sum(RHC.D0$z*RHC.D0$omega1.att)
RHC.D0$dem0.att <- sum((1-RHC.D0$z)*RHC.D0$omega0.att)

(sum(RHC.D0$dth30*RHC.D0$z*RHC.D0$omega1.att)/RHC.D0$dem1.att)[1] - (sum(RHC.D0$dth30*(1-RHC.D0$z)*(RHC.D0$omega0.att)/RHC.D0$dem0.att)[1])
```

#WATE using overlap weights

```{r}
RHC.D0$omega1.overlap <- 1-RHC.D0$ps
RHC.D0$omega0.overlap <- RHC.D0$ps
RHC.D0$dem1.overlap <- sum(RHC.D0$z*RHC.D0$omega1.overlap)
RHC.D0$dem0.overlap <- sum((1-RHC.D0$z)*RHC.D0$omega0.overlap)

(sum(RHC.D0$dth30*RHC.D0$z*RHC.D0$omega1.overlap)/RHC.D0$dem1.overlap)[1] - (sum(RHC.D0$dth30*(1-RHC.D0$z)*(RHC.D0$omega0.overlap)/RHC.D0$dem0.overlap)[1])
```

#WATE using ATT weights and truncated propensity scores between 0.1 and 0.9

```{r}
RHC.D0.trunc$omega1.att <- 1
RHC.D0.trunc$omega0.att <- RHC.D0.trunc$ps/(1-RHC.D0.trunc$ps)
RHC.D0.trunc$dem1.att <- sum(RHC.D0.trunc$z*RHC.D0.trunc$omega1.att)
RHC.D0.trunc$dem0.att <- sum((1-RHC.D0.trunc$z)*RHC.D0.trunc$omega0.att)

(sum(RHC.D0.trunc$dth30*RHC.D0.trunc$z*RHC.D0.trunc$omega1.att)/RHC.D0.trunc$dem1.att)[1] - (sum(RHC.D0.trunc$dth30*(1-RHC.D0.trunc$z)*(RHC.D0.trunc$omega0.att)/RHC.D0.trunc$dem0.att)[1])
```


####Finding Standard Errors of all estimation methods

#Defining omegas and denominators for all effect measurements

```{r}
dem.omega <- function(data){
  #No Weights
  data$dem1.nw <- sum(data$z)
  data$dem0.nw <- sum(1-data$z)

  #ATE
  data$omega1.ate <- 1/data$ps
  data$omega0.ate <- 1/(1-data$ps)
  data$dem1.ate <- sum(data$z*data$omega1.ate)
  data$dem0.ate <- sum((1-data$z)*data$omega0.ate)
  
  #ATT
  data$omega1.att <- 1
  data$omega0.att <- data$ps/(1-data$ps)
  data$dem1.att <- sum(data$z*data$omega1.att)
  data$dem0.att <- sum((1-data$z)*data$omega0.att)
  
  #Overlap
  data$omega1.overlap <- 1-data$ps
  data$omega0.overlap <- data$ps
  data$dem1.overlap <- sum(data$z*data$omega1.overlap)
  data$dem0.overlap <- sum((1-data$z)*data$omega0.overlap)
  
  return(data)
}
```

#Truncating Function
```{r}
trunc <- function(data){  
  RHC.D.trunc <- data
  ps.order.trunc <- order(RHC.D.trunc$ps)
  
  RHC.D0.trunc <- RHC.D.trunc[ps.order.trunc,]
  
  max <- max(which(RHC.D0.trunc$ps < 0.1))
  min <- min(which(RHC.D0.trunc$ps > 0.9))
  
  RHC.D0.trunc <- RHC.D0.trunc[-c(min:5735),]
  RHC.D0.trunc <- RHC.D0.trunc[-c(1:max),]
  
  RHC.D0.trunc$omega1.att <- 1
  RHC.D0.trunc$omega0.att <- RHC.D0.trunc$ps/(1-RHC.D0.trunc$ps)
  RHC.D0.trunc$dem1.att <- sum(RHC.D0.trunc$z*RHC.D0.trunc$omega1.att)
  RHC.D0.trunc$dem0.att <- sum((1-RHC.D0.trunc$z)*RHC.D0.trunc$omega0.att)
  
  return(RHC.D0.trunc)
}
```

#WATE function for all effect types

```{r}
wate <- function(data){
  #No Weights
  a <- ((sum(data$dth30*data$z)/data$dem1.nw)[1] - (sum(data$dth30*(1-data$z))/data$dem0.nw)[1])

  #ATE
  b <- (sum(data$dth30*data$z*data$omega1.ate)/data$dem1.ate)[1] - (sum(data$dth30*(1-data$z)*(data$omega0.ate)/data$dem0.ate)[1])
  
  #ATT
  c <- (sum(data$dth30*data$z*data$omega1.att)/data$dem1.att)[1] - (sum(data$dth30*(1-data$z)*(data$omega0.att)/data$dem0.att)[1])
  
  #Overlap
  d <- (sum(data$dth30*data$z*data$omega1.overlap)/data$dem1.overlap)[1] - (sum(data$dth30*(1-data$z)*(data$omega0.overlap))/data$dem0.overlap)[1]
  
  #Truncated ATT
  trunc.data <- trunc(data)
  e <- (sum(trunc.data$dth30*trunc.data$z*trunc.data$omega1.att)/trunc.data$dem1.att)[1] - (sum(trunc.data$dth30*(1-trunc.data$z)*(trunc.data$omega0.att)/trunc.data$dem0.att)[1])
    
  return(c(a,b,c,d,e))
}
```



#Bootstrapping function

```{r}
model.boot <- function(n){
  i <- sample(1:n, size=n, replace=TRUE)
  RHC.D.boot <- RHC.D[i,]
  psmod.boot <- glm(swang1 ~ age + sex + edu + das2d3pc + dnr1 + surv2md1 + aps1 + scoma1 + wtkilo1 + temp1 + meanbp1 + resp1 + hrt1 + pafi1 + paco21 + ph1 + wblc1 + hema1 + sod1 + pot1 + crea1 + bili1 + alb1 + resp + card +    neuro + gastr + renal + meta + hema + seps + trauma + ortho + cardiohx + chfhx + dementhx + psychhx + chrpulhx + renalhx + liverhx + gibledhx + malighx + immunhx + transhx + amihx +
  cat1_MOSF.w.Sepsis  +  cat1_MOSF.w.Malignancy  +   cat1_ARF  + cat1_CHF +  cat1_Coma +  cat1_Cirrhosis  + cat1_Lung.Cancer +   cat1_Colon.Cancer + cat2_MOSF.w.Sepsis + cat2_Coma + cat2_MOSF.w.Malignancy + cat2_Lung.Cancer +   cat2_Cirrhosis + cat2_Colon.Cancer + ca_No + ca_Metastatic  + ninsclas_Private._.Medicare + ninsclas_Private  + ninsclas_Medicaid   + ninsclas_No.insurance + ninsclas_Medicare._.Medicaid + race_black + race_other  +         income_25_50k + income_11_25k  + income_50k,
               family  = binomial(link = "logit"),
               data    = RHC.D.boot)
  RHC.D.boot$ps <- predict(psmod.boot, type = "response")
  RHC.wate <- dem.omega(RHC.D.boot)
  WATE <- wate(RHC.wate)
  return(WATE)
}

#Function Test
model.boot(5735)

#Running the function
n <- 5735
B <- 100

set.seed(1234)
wate.star <- replicate(B, expr = model.boot(n), simplify = TRUE)
(se.wate.nw.star <- sd(wate.star[1,]))
(se.wate.ate.star <- sd(wate.star[2,]))
(se.wate.att.star <- sd(wate.star[3,]))
(se.wate.overlap.star <- sd(wate.star[4,]))
(se.wate.truncatt.star <- sd(wate.star[5,]))
```



