---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages

```{r}
## helper
library(ggplot2)
library(dplyr)
library(tidyr)
library(stringr)
library(magrittr)
library(plyr)
library(mvtnorm)
library(Rlab)
library(plotrix)

## Load Matching for PS matching
library(Matching)
## Load FastDummies
library(fastDummies)
```

## Simulation from Li, Thomas, and Li

## Developing the simulation model

```{r}
#Generating the multivariate random varible
gen <- function(n){
  mean <- c(0,0,0,0,0,0)
  sigma <- matrix(c(1,0.5,0.5,0.5,0.5,0.5,
                  0.5,1,0.5,0.5,0.5,0.5,
                  0.5,0.5,1,0.5,0.5,0.5,
                  0.5,0.5,0.5,1,0.5,0.5,
                  0.5,0.5,0.5,0.5,1,0.5,
                  0.5,0.5,0.5,0.5,0.5,1),
                ncol = 6)
  v <- rmvnorm(n, mean=mean, sigma=sigma)
  #Keeping first three covariates the same, making last three covariates binary
  x1 <- v[,1]
  x2 <- v[,2]
  x3 <- v[,3]
  x4 <- as.numeric(v[,4] < 0)
  x5 <- as.numeric(v[,5] < 0)
  x6 <- as.numeric(v[,6] < 0)
  x <- data.frame(x1, x2, x3, x4, x5, x6)
  return(x)
}

ps.model <- function(data, gamma, treat.prev, n){
  e <- numeric(n) 
  for(i in 1:n){
    e[i] <- (1 + exp(-(treat.prev + .15*gamma*data[i,1] + 0.3*gamma*data[i,2] + 0.3*gamma*data[i,3]
                        - 0.2*gamma*data[i,4] - 0.25*gamma*data[i,5] - 0.25*gamma*data[i,6])))^-1
  }
  return(e)
}

#Simulating observed treatment values
treat.assign <- function(ps, n){
  z <- numeric(n)
  for(i in 1:n){
    z[i] <- rbern(1, ps[i])
  }
  return(z)
}

#Outcome model

outcomeModel <- function(data, z, n){
  y <- numeric(n)
  for(i in 1:n){
    y[i] <- (-0.5*data[i,1] - 0.5*data[i,2] - 1.5*data[i,3] 
    + 0.8*data[i,4] + 0.8*data[i,5] + 1.0*data[i,6]
    + 0.75*z[i] + rnorm(1, mean=0, sd=1.5)) 
  }
  return(y)
}

data <- function(gamma, treat.prev, n){
  x <- gen(n)
  ps <- ps.model(x,gamma,treat.prev, n)
  z <- treat.assign(ps,n)
  y <- outcomeModel(x,z,n)
  x <- data.frame(x, ps, z, y)
  return(x)
}

x <- data(2,0.4,500)
```

##Crude Estimate
```{r}
crude <- function(gamma, treat.prev, n){
  x <- data(gamma,treat.prev,n)
  crude <- (sum(x[,8]*x[,9])/sum(x[,8])) - (sum((1-x[,8])*x[,9])/sum((1-x[,8])))
  return(crude)
}
```

## Overlap Weighting
```{r}
omega.ol <- function(data, n){
  w.ol <- numeric(n)
  for(i in 1:n){
    if(data[i,8] == 1){
      w.ol[i] <- 1-data[i,7]
    }
    else if(data[i,8] == 0){
      w.ol[i] <- data[i,7]
    }
  }
  return(w.ol)
}

overlap <- function(gamma, treat.prev, n){
  x <- data(gamma,treat.prev,n)
  omega_ol <- omega.ol(x,n)
  x <- data.frame(x,omega_ol)
  (overlap <- (sum(x[,8]*x[,9]*x[,10])/sum(x[,8]*x[,10])) - 
  sum((1-x[,8])*x[,9]*x[,10])/sum((1-x[,8])*x[,10]))
  return(overlap)
}

(overlap.bias <- overlap(1,0.4,500))
```

##Inverse Probability Weighting
```{r}
#Calculating Weights
omega.ipw <- function(data, n){
  w.ipw <- numeric(n)
  for(i in 1:n){
    if(data[i,8] == 1){
      w.ipw[i] <- 1/data[i,7]
    }
    else if(data[i,8] == 0){
      w.ipw[i] <- 1/(1-data[i,7])
    }
  }
  return(w.ipw)
}

#Calculating treatment effects using IPW and finding its bias 
ipw <- function(gamma, treat.prev, n){
  x <- data(gamma,treat.prev,n)
  omega_ipw <- omega.ipw(x,n)
  x <- data.frame(x,omega_ipw)
  ipw <- (sum(x[,8]*x[,9]*x[,10])/sum(x[,8]*x[,10])) - 
  (sum((1-x[,8])*x[,9]*x[,10])/sum((1-x[,8])*x[,10]))
  return(ipw)
}

(bias.ipw <- ipw(2,0.4,500))
```


##Symmetric Trimmed IPW
```{r}
#Truncating PS Values
sym.trim <- function(data, alpha,n){
  ps.order <- order(data[,7])
  data.trunc <- data[ps.order,]

  max <- max(which(data.trunc[,7] < alpha))
  min <- min(which(data.trunc[,7] > (1-alpha)))

  if(max == -Inf | min == Inf){
    data.trunc <- data.trunc
  }else if (max | min != "NA"){
    data.trunc <- data.trunc[-c(min:n),]
    data.trunc <- data.trunc[-c(1:max),]
  }
  return(data.trunc)
}

#Calculating symmetric trimmed IPW weights
omega.ipw.trim <- function(data, n){
  w.ipw.trim <- numeric(n)
  for(i in 1:n){
    if(data[i,8] == 1){
      w.ipw.trim[i] <- 1/data[i,7]
    }
    else if(data[i,8] == 0){
      w.ipw.trim[i] <- 1/(1-data[i,7])
    }
  }
  return(w.ipw.trim)
}

ipw.trim <- function(gamma, treat.prev, alpha, n){
  x <- data(gamma,treat.prev,n)
  x.trunc <- sym.trim(x,alpha,n)
  n2 <- length(x.trunc[,1])
  omega_ipw_trim <- omega.ipw.trim(x.trunc,n2)
  x.trunc <- data.frame(x.trunc,omega_ipw_trim)
  (ipw.trim <- (sum(x.trunc[,8]*x.trunc[,9]*x.trunc[,10])/sum(x.trunc[,8]*x.trunc[,10])) -
  (sum((1-x.trunc[,8])*x.trunc[,9]*x.trunc[,10])/sum((1-x.trunc[,8])*x.trunc[,10])))
  return(ipw.trim)
}

(x.trunc <- ipw.trim(1,0.4,0.15,500))
```

##Asymmetric Trimmed IPW

```{r}
asym.trim <- function(data,q,n){
  #Step 1 - Trimming non-overlap points
  ps.order.atrunc <- order(data[,7])
  data.atrunc <- data[ps.order.atrunc,]
  tail(data.atrunc)
  
  (control.max <- max(which(data.atrunc[,8] == 0)))
  (treat.min <- min(which(data.atrunc[,8] == 1)))
  
  if(control.max != n){
    data.atrunc <- data.atrunc[-c((control.max+1):n),]
  } else if (control.max == n){
    data.atrunc <- data.atrunc
  }

  if(treat.min != 1){
    data.atrunc <- data.atrunc[-c(1:(treat.min-1)),]
  } else if(treat.min == 1){
    data.atrunc <- data.atrunc
  }
  
  #Step 2 - Trim based on given quantiles if q > 0
  if(q > 0){
    z.order.atrunc <- order(data.atrunc[,8])
    data.atrunc <- data.atrunc[z.order.atrunc,]
    
    (z0.max <- max(which(data.atrunc[,8] == 0)))
    (z1.min <- min(which(data.atrunc[,8] == 1)))
    
    (z0.quant.value <- quantile(data.atrunc[1:z0.max,7], (1-q))) 
    (z1.quant.value <- quantile(data.atrunc[z1.min:dim(data.atrunc)[1],7], q))
    
    (z0.trim <- which(data.atrunc[,8] == 0 & data.atrunc[,7] > z0.quant.value))
    (z1.trim <- which(data.atrunc[,8] == 1 & data.atrunc[,7] < z1.quant.value))
    
    data.atrunc <- data.atrunc[-c(z0.trim, z1.trim),]
  } else data.atrunc <- data.atrunc
}

##Asymmetric Trimmed IPw Weights

omega.ipw.atrim <- function(data, n){
  w.ipw.atrim <- numeric(n)
  for(i in 1:n){
    if(data[i,8] == 1){
      w.ipw.atrim[i] <- 1/data[i,7]
    }
    else if(data[i,8] == 0){
      w.ipw.atrim[i] <- 1/(1-data[i,7])
    }
  }
  return(w.ipw.atrim)
}

#Calculating ATE with IPW and its bias
ipw.atrim <- function(gamma, treat.prev, q, n){
  x <- data(gamma,treat.prev,n)
  x.atrunc <- asym.trim(x,q,n)
  n2 <- length(x.atrunc[,1])
  omega_ipw_atrim <- omega.ipw.atrim(x.atrunc,n2)
  x.atrunc <- data.frame(x.atrunc,omega_ipw_atrim)
  (ipw.atrim <- (sum(x.atrunc[,8]*x.atrunc[,9]*x.atrunc[,10])/sum(x.atrunc[,8]*x.atrunc[,10])) - 
  (sum((1-x.atrunc[,8])*x.atrunc[,9]*x.atrunc[,10])/sum((1-x.atrunc[,8])*x.atrunc[,10])))
  return(ipw.atrim)
}

(x.atrunc.bias <- ipw.atrim(1,0.4,0.05,500))
```

##Bias function containing all possible methods

###NOTE: Set the seed before each individual simulation

```{r}
set.seed(1234)
bias <- function(gamma, treat.prev, crude, overlap, ipw, sym.trim, alpha, asym.trim, q, n){
  if(crude == T && overlap == F && ipw == F && sym.trim == F && asym.trim == F){
    crude.rep <- replicate(1000, expr = crude(gamma,treat.prev,n))
    return(mean(crude.rep)-0.75)
  } else if(crude == F && overlap == T && ipw == F && sym.trim == F && asym.trim == F){
    overlap.rep <- replicate(1000, expr = overlap(gamma,treat.prev,n))
    return(mean(overlap.rep)-0.75)
  } else if(crude == F && overlap == F && ipw == T && sym.trim == F && asym.trim == F){
    ipw.rep <- replicate(1000, expr = ipw(gamma,treat.prev,n))
    return(mean(ipw.rep)-0.75)
  } else if(crude == F && overlap == F && ipw == F && sym.trim == T && asym.trim == F){
    ipw.trim.rep <- replicate(1000, expr = ipw.trim(gamma,treat.prev,alpha,n))
    return(mean(ipw.trim.rep)-0.75)
  } else if(crude == F && overlap == F && ipw == F && sym.trim == F && asym.trim == T){
    ipw.atrim.rep <- replicate(1000, expr = ipw.atrim(gamma,treat.prev,q,n))
    return(mean(ipw.atrim.rep)-0.75)
  }
}

##n = 500
 #Treatment Prevalence = 0.4

  #Crude Estimator
set.seed(1234)
(Bias.crude.g1.tp4 <- bias(1,0.4,T,F,F,F,0,F,0,500))
(Bias.crude.g2.tp4 <- bias(2,0.4,T,F,F,F,0,F,0,500))
(Bias.crude.g3.tp4 <- bias(3,0.4,T,F,F,F,0,F,0,500))
(Bias.crude.g4.tp4 <- bias(4,0.4,T,F,F,F,0,F,0,500))

  #Overlap Estimator
set.seed(1234)
(Bias.ov.g1.tp4 <- bias(1,0.4,F,T,F,F,0,F,0,500))
(Bias.ov.g2.tp4 <- bias(2,0.4,F,T,F,F,0,F,0,500))
(Bias.ov.g3.tp4 <- bias(3,0.4,F,T,F,F,0,F,0,500))
(Bias.ov.g4.tp4 <- bias(4,0.4,F,T,F,F,0,F,0,500))

  #IPW With no Trim
set.seed(1234)
(Bias.ipw.g1.tp4 <- bias(1,0.4,F,F,T,F,0,F,0,500))
(Bias.ipw.g2.tp4 <- bias(2,0.4,F,F,T,F,0,F,0,500))
(Bias.ipw.g3.tp4 <- bias(3,0.4,F,F,T,F,0,F,0,500))
(Bias.ipw.g4.tp4 <- bias(4,0.4,F,F,T,F,0,F,0,500))

#IPW With Symmetric Trim and alpha = 0.05
set.seed(1234)
(Bias.symtrim.a5.g1.tp4 <- bias(1,0.4,F,F,F,T,0.05,F,0,500))
(Bias.symtrim.a5.g2.tp4 <- bias(2,0.4,F,F,F,T,0.05,F,0,500))
(Bias.symtrim.a5.g3.tp4 <- bias(3,0.4,F,F,F,T,0.05,F,0,500))
(Bias.symtrim.a5.g4.tp4 <- bias(4,0.4,F,F,F,T,0.05,F,0,500))

#IPW With Symmetric Trim and alpha = 0.10
set.seed(1234)
(Bias.symtrim.a10.g1.tp4 <- bias(1,0.4,F,F,F,T,0.10,F,0,500))
(Bias.symtrim.a10.g2.tp4 <- bias(2,0.4,F,F,F,T,0.10,F,0,500))
(Bias.symtrim.a10.g3.tp4 <- bias(3,0.4,F,F,F,T,0.10,F,0,500))
(Bias.symtrim.a10.g4.tp4 <- bias(4,0.4,F,F,F,T,0.10,F,0,500))

#IPW With Symmetric Trim and alpha = 0.15
set.seed(1234)
(Bias.symtrim.a15.g1.tp4 <- bias(1,0.4,F,F,F,T,0.15,F,0,500))
(Bias.symtrim.a15.g2.tp4 <- bias(2,0.4,F,F,F,T,0.15,F,0,500))
(Bias.symtrim.a15.g3.tp4 <- bias(3,0.4,F,F,F,T,0.15,F,0,500))
(Bias.symtrim.a15.g4.tp4 <- bias(4,0.4,F,F,F,T,0.15,F,0,500))

#IPW With Asymmetric Trim and q = 0
set.seed(1234)
(Bias.asymtrim.q0.g1.tp4 <- bias(1,0.4,F,F,F,F,0,T,0,500))
(Bias.asymtrim.q0.g2.tp4 <- bias(2,0.4,F,F,F,F,0,T,0,500))
(Bias.asymtrim.q0.g3.tp4 <- bias(3,0.4,F,F,F,F,0,T,0,500))
(Bias.asymtrim.q0.g4.tp4 <- bias(4,0.4,F,F,F,F,0,T,0,500))

#IPW With Asymmetric Trim and q = 0.01
set.seed(1234)
(Bias.asymtrim.q1.g1.tp4 <- bias(1,0.4,F,F,F,F,0,T,0.01,500))
(Bias.asymtrim.q1.g2.tp4 <- bias(2,0.4,F,F,F,F,0,T,0.01,500))
(Bias.asymtrim.q1.g3.tp4 <- bias(3,0.4,F,F,F,F,0,T,0.01,500))
(Bias.asymtrim.q1.g4.tp4 <- bias(4,0.4,F,F,F,F,0,T,0.01,500))

#IPW With Asymmetric Trim and q = 0.05
set.seed(1234)
(Bias.asymtrim.q5.g1.tp4 <- bias(1,0.4,F,F,F,F,0,T,0.05,500))
(Bias.asymtrim.q5.g2.tp4 <- bias(2,0.4,F,F,F,F,0,T,0.05,500))
(Bias.asymtrim.q5.g3.tp4 <- bias(3,0.4,F,F,F,F,0,T,0.05,500))
(Bias.asymtrim.q5.g4.tp4 <- bias(4,0.4,F,F,F,F,0,T,0.05,500))

##n = 500
 #Treatment Prevalence = 0.1

  #Crude Estimator
set.seed(1234)
(Bias.crude.g1.tp1 <- bias(1,0.1,T,F,F,F,0,F,0,500))
(Bias.crude.g2.tp1 <- bias(2,0.1,T,F,F,F,0,F,0,500))
(Bias.crude.g3.tp1 <- bias(3,0.1,T,F,F,F,0,F,0,500))
(Bias.crude.g4.tp1 <- bias(4,0.1,T,F,F,F,0,F,0,500))

  #Overlap Estimator
set.seed(1234)
(Bias.ov.g1.tp1 <- bias(1,0.1,F,T,F,F,0,F,0,500))
(Bias.ov.g2.tp1 <- bias(2,0.1,F,T,F,F,0,F,0,500))
(Bias.ov.g3.tp1 <- bias(3,0.1,F,T,F,F,0,F,0,500))
(Bias.ov.g4.tp1 <- bias(4,0.1,F,T,F,F,0,F,0,500))

  #IPW With no Trim
set.seed(1234)
(Bias.ipw.g1.tp1 <- bias(1,0.1,F,F,T,F,0,F,0,500))
(Bias.ipw.g2.tp1 <- bias(2,0.1,F,F,T,F,0,F,0,500))
(Bias.ipw.g3.tp1 <- bias(3,0.1,F,F,T,F,0,F,0,500))
(Bias.ipw.g4.tp1 <- bias(4,0.1,F,F,T,F,0,F,0,500))

#IPW With Symmetric Trim and alpha = 0.05
set.seed(1234)
(Bias.symtrim.a5.g1.tp1 <- bias(1,0.1,F,F,F,T,0.05,F,0,500))
(Bias.symtrim.a5.g2.tp1 <- bias(2,0.1,F,F,F,T,0.05,F,0,500))
(Bias.symtrim.a5.g3.tp1 <- bias(3,0.1,F,F,F,T,0.05,F,0,500))
(Bias.symtrim.a5.g4.tp1 <- bias(4,0.1,F,F,F,T,0.05,F,0,500))

#IPW With Symmetric Trim and alpha = 0.10
set.seed(1234)
(Bias.symtrim.a10.g1.tp1 <- bias(1,0.1,F,F,F,T,0.10,F,0,500))
(Bias.symtrim.a10.g2.tp1 <- bias(2,0.1,F,F,F,T,0.10,F,0,500))
(Bias.symtrim.a10.g3.tp1 <- bias(3,0.1,F,F,F,T,0.10,F,0,500))
(Bias.symtrim.a10.g4.tp1 <- bias(4,0.1,F,F,F,T,0.10,F,0,500))

#IPW With Symmetric Trim and alpha = 0.15
set.seed(1234)
(Bias.symtrim.a15.g1.tp1 <- bias(1,0.1,F,F,F,T,0.15,F,0,500))
(Bias.symtrim.a15.g2.tp1 <- bias(2,0.1,F,F,F,T,0.15,F,0,500))
(Bias.symtrim.a15.g3.tp1 <- bias(3,0.1,F,F,F,T,0.15,F,0,500))
(Bias.symtrim.a15.g4.tp1 <- bias(4,0.1,F,F,F,T,0.15,F,0,500))

#IPW With Asymmetric Trim and q = 0
set.seed(1234)
(Bias.asymtrim.q0.g1.tp1 <- bias(1,0.1,F,F,F,F,0,T,0,500))
(Bias.asymtrim.q0.g2.tp1 <- bias(2,0.1,F,F,F,F,0,T,0,500))
(Bias.asymtrim.q0.g3.tp1 <- bias(3,0.1,F,F,F,F,0,T,0,500))
(Bias.asymtrim.q0.g4.tp1 <- bias(4,0.1,F,F,F,F,0,T,0,500))

#IPW With Asymmetric Trim and q = 0.01
set.seed(1234)
(Bias.asymtrim.q1.g1.tp1 <- bias(1,0.1,F,F,F,F,0,T,0.01,500))
(Bias.asymtrim.q1.g2.tp1 <- bias(2,0.1,F,F,F,F,0,T,0.01,500))
(Bias.asymtrim.q1.g3.tp1 <- bias(3,0.1,F,F,F,F,0,T,0.01,500))
(Bias.asymtrim.q1.g4.tp1 <- bias(4,0.1,F,F,F,F,0,T,0.01,500))

#IPW With Asymmetric Trim and q = 0.05
set.seed(1234)
(Bias.asymtrim.q5.g1.tp1 <- bias(1,0.1,F,F,F,F,0,T,0.05,500))
(Bias.asymtrim.q5.g2.tp1 <- bias(2,0.1,F,F,F,F,0,T,0.05,500))
(Bias.asymtrim.q5.g3.tp1 <- bias(3,0.1,F,F,F,F,0,T,0.05,500))
(Bias.asymtrim.q5.g4.tp1 <- bias(4,0.1,F,F,F,F,0,T,0.05,500))
```

#Function for computing RMSE of all methods

###NOTE: Set the seed before each individual simulation

```{r}
set.seed(1234)
rmse <- function(gamma, treat.prev, crude, overlap, ipw, sym.trim, alpha, asym.trim, q, n){
  if(crude == T && overlap == F && ipw == F && sym.trim == F && asym.trim == F){
    crude.rep <- replicate(1000, expr = crude(gamma,treat.prev,n))
    return(sqrt(var(crude.rep) + (mean(crude.rep)-0.75)^2))
  } else if(crude == F && overlap == T && ipw == F && sym.trim == F && asym.trim == F){
    overlap.rep <- replicate(1000, expr = overlap(gamma,treat.prev,n))
    return(sqrt(var(overlap.rep) + (mean(overlap.rep)-0.75)^2))
  } else if(crude == F && overlap == F && ipw == T && sym.trim == F && asym.trim == F){
    ipw.rep <- replicate(1000, expr = ipw(gamma,treat.prev,n))
    return(sqrt(var(ipw.rep) + (mean(ipw.rep)-0.75)^2))
  } else if(crude == F && overlap == F && ipw == F && sym.trim == T && asym.trim == F){
    ipw.trim.rep <- replicate(1000, expr = ipw.trim(gamma,treat.prev,alpha,n))
    return(sqrt(var(ipw.trim.rep) + (mean(ipw.trim.rep)-0.75)^2))
  } else if(crude == F && overlap == F && ipw == F && sym.trim == F && asym.trim == T){
    ipw.atrim.rep <- replicate(1000, expr = ipw.atrim(gamma,treat.prev,q,n))
    return(sqrt(var(ipw.atrim.rep) + (mean(ipw.atrim.rep)-0.75)^2))
  }
}

##n = 500
 #Treatment Prevalence = 0.4

  #Crude Estimator
set.seed(1234)
(rmse.crude.g1.tp4 <- rmse(1,0.4,T,F,F,F,0,F,0,500))
(rmse.crude.g2.tp4 <- rmse(2,0.4,T,F,F,F,0,F,0,500))
(rmse.crude.g3.tp4 <- rmse(3,0.4,T,F,F,F,0,F,0,500))
(rmse.crude.g4.tp4 <- rmse(4,0.4,T,F,F,F,0,F,0,500))

  #Overlap Estimator
set.seed(1234)
(rmse.ov.g1.tp4 <- rmse(1,0.4,F,T,F,F,0,F,0,500))
(rmse.ov.g2.tp4 <- rmse(2,0.4,F,T,F,F,0,F,0,500))
(rmse.ov.g3.tp4 <- rmse(3,0.4,F,T,F,F,0,F,0,500))
(rmse.ov.g4.tp4 <- rmse(4,0.4,F,T,F,F,0,F,0,500))

  #IPW With no Trim
set.seed(1234)
(rmse.ipw.g1.tp4 <- rmse(1,0.4,F,F,T,F,0,F,0,500))
(rmse.ipw.g2.tp4 <- rmse(2,0.4,F,F,T,F,0,F,0,500))
(rmse.ipw.g3.tp4 <- rmse(3,0.4,F,F,T,F,0,F,0,500))
(rmse.ipw.g4.tp4 <- rmse(4,0.4,F,F,T,F,0,F,0,500))

#IPW With Symmetric Trim and alpha = 0.05
set.seed(1234)
(rmse.symtrim.a5.g1.tp4 <- rmse(1,0.4,F,F,F,T,0.05,F,0,500))
(rmse.symtrim.a5.g2.tp4 <- rmse(2,0.4,F,F,F,T,0.05,F,0,500))
(rmse.symtrim.a5.g3.tp4 <- rmse(3,0.4,F,F,F,T,0.05,F,0,500))
(rmse.symtrim.a5.g4.tp4 <- rmse(4,0.4,F,F,F,T,0.05,F,0,500))

#IPW With Symmetric Trim and alpha = 0.10
set.seed(1234)
(rmse.symtrim.a10.g1.tp4 <- rmse(1,0.4,F,F,F,T,0.10,F,0,500))
(rmse.symtrim.a10.g2.tp4 <- rmse(2,0.4,F,F,F,T,0.10,F,0,500))
(rmse.symtrim.a10.g3.tp4 <- rmse(3,0.4,F,F,F,T,0.10,F,0,500))
(rmse.symtrim.a10.g4.tp4 <- rmse(4,0.4,F,F,F,T,0.10,F,0,500))

#IPW With Symmetric Trim and alpha = 0.15
set.seed(1234)
(rmse.symtrim.a15.g1.tp4 <- rmse(1,0.4,F,F,F,T,0.15,F,0,500))
(rmse.symtrim.a15.g2.tp4 <- rmse(2,0.4,F,F,F,T,0.15,F,0,500))
(rmse.symtrim.a15.g3.tp4 <- rmse(3,0.4,F,F,F,T,0.15,F,0,500))
(rmse.symtrim.a15.g4.tp4 <- rmse(4,0.4,F,F,F,T,0.15,F,0,500))

#IPW With Asymmetric Trim and q = 0
set.seed(1234)
(rmse.asymtrim.q0.g1.tp4 <- rmse(1,0.4,F,F,F,F,0,T,0,500))
(rmse.asymtrim.q0.g2.tp4 <- rmse(2,0.4,F,F,F,F,0,T,0,500))
(rmse.asymtrim.q0.g3.tp4 <- rmse(3,0.4,F,F,F,F,0,T,0,500))
(rmse.asymtrim.q0.g4.tp4 <- rmse(4,0.4,F,F,F,F,0,T,0,500))

#IPW With Asymmetric Trim and q = 0.01
set.seed(1234)
(rmse.asymtrim.q1.g1.tp4 <- rmse(1,0.4,F,F,F,F,0,T,0.01,500))
(rmse.asymtrim.q1.g2.tp4 <- rmse(2,0.4,F,F,F,F,0,T,0.01,500))
(rmse.asymtrim.q1.g3.tp4 <- rmse(3,0.4,F,F,F,F,0,T,0.01,500))
(rmse.asymtrim.q1.g4.tp4 <- rmse(4,0.4,F,F,F,F,0,T,0.01,500))

#IPW With Asymmetric Trim and q = 0.05
set.seed(1234)
(rmse.asymtrim.q5.g1.tp4 <- rmse(1,0.4,F,F,F,F,0,T,0.05,500))
(rmse.asymtrim.q5.g2.tp4 <- rmse(2,0.4,F,F,F,F,0,T,0.05,500))
(rmse.asymtrim.q5.g3.tp4 <- rmse(3,0.4,F,F,F,F,0,T,0.05,500))
(rmse.asymtrim.q5.g4.tp4 <- rmse(4,0.4,F,F,F,F,0,T,0.05,500))

 #Treatment Prevalence = 0.1

  #Crude Estimator
set.seed(1234)
(rmse.crude.g1.tp1 <- rmse(1,0.1,T,F,F,F,0,F,0,500))
(rmse.crude.g2.tp1 <- rmse(2,0.1,T,F,F,F,0,F,0,500))
(rmse.crude.g3.tp1 <- rmse(3,0.1,T,F,F,F,0,F,0,500))
(rmse.crude.g4.tp1 <- rmse(4,0.1,T,F,F,F,0,F,0,500))

  #Overlap Estimator
set.seed(1234)
(rmse.ov.g1.tp1 <- rmse(1,0.1,F,T,F,F,0,F,0,500))
(rmse.ov.g2.tp1 <- rmse(2,0.1,F,T,F,F,0,F,0,500))
(rmse.ov.g3.tp1 <- rmse(3,0.1,F,T,F,F,0,F,0,500))
(rmse.ov.g4.tp1 <- rmse(4,0.1,F,T,F,F,0,F,0,500))

  #IPW With no Trim
set.seed(1234)
(rmse.ipw.g1.tp1 <- rmse(1,0.1,F,F,T,F,0,F,0,500))
(rmse.ipw.g2.tp1 <- rmse(2,0.1,F,F,T,F,0,F,0,500))
(rmse.ipw.g3.tp1 <- rmse(3,0.1,F,F,T,F,0,F,0,500))
(rmse.ipw.g4.tp1 <- rmse(4,0.1,F,F,T,F,0,F,0,500))

#IPW With Symmetric Trim and alpha = 0.05
set.seed(1234)
(rmse.symtrim.a5.g1.tp1 <- rmse(1,0.1,F,F,F,T,0.05,F,0,500))
(rmse.symtrim.a5.g2.tp1 <- rmse(2,0.1,F,F,F,T,0.05,F,0,500))
(rmse.symtrim.a5.g3.tp1 <- rmse(3,0.1,F,F,F,T,0.05,F,0,500))
(rmse.symtrim.a5.g4.tp1 <- rmse(4,0.1,F,F,F,T,0.05,F,0,500))

#IPW With Symmetric Trim and alpha = 0.10
set.seed(1234)
(rmse.symtrim.a10.g1.tp1 <- rmse(1,0.1,F,F,F,T,0.10,F,0,500))
(rmse.symtrim.a10.g2.tp1 <- rmse(2,0.1,F,F,F,T,0.10,F,0,500))
(rmse.symtrim.a10.g3.tp1 <- rmse(3,0.1,F,F,F,T,0.10,F,0,500))
(rmse.symtrim.a10.g4.tp1 <- rmse(4,0.1,F,F,F,T,0.10,F,0,500))

#IPW With Symmetric Trim and alpha = 0.15
set.seed(1234)
(rmse.symtrim.a15.g1.tp1 <- rmse(1,0.1,F,F,F,T,0.15,F,0,500))
(rmse.symtrim.a15.g2.tp1 <- rmse(2,0.1,F,F,F,T,0.15,F,0,500))
(rmse.symtrim.a15.g3.tp1 <- rmse(3,0.1,F,F,F,T,0.15,F,0,500))
(rmse.symtrim.a15.g4.tp1 <- rmse(4,0.1,F,F,F,T,0.15,F,0,500))

#IPW With Asymmetric Trim and q = 0
set.seed(1234)
(rmse.asymtrim.q0.g1.tp1 <- rmse(1,0.1,F,F,F,F,0,T,0,500))
(rmse.asymtrim.q0.g2.tp1 <- rmse(2,0.1,F,F,F,F,0,T,0,500))
(rmse.asymtrim.q0.g3.tp1 <- rmse(3,0.1,F,F,F,F,0,T,0,500))
(rmse.asymtrim.q0.g4.tp1 <- rmse(4,0.1,F,F,F,F,0,T,0,500))

#IPW With Asymmetric Trim and q = 0.01
set.seed(1234)
(rmse.asymtrim.q1.g1.tp1 <- rmse(1,0.1,F,F,F,F,0,T,0.01,500))
(rmse.asymtrim.q1.g2.tp1 <- rmse(2,0.1,F,F,F,F,0,T,0.01,500))
(rmse.asymtrim.q1.g3.tp1 <- rmse(3,0.1,F,F,F,F,0,T,0.01,500))
(rmse.asymtrim.q1.g4.tp1 <- rmse(4,0.1,F,F,F,F,0,T,0.01,500))

#IPW With Asymmetric Trim and q = 0.05
set.seed(1234)
(rmse.asymtrim.q5.g1.tp1 <- rmse(1,0.1,F,F,F,F,0,T,0.05,500))
(rmse.asymtrim.q5.g2.tp1 <- rmse(2,0.1,F,F,F,F,0,T,0.05,500))
(rmse.asymtrim.q5.g3.tp1 <- rmse(3,0.1,F,F,F,F,0,T,0.05,500))
(rmse.asymtrim.q5.g4.tp1 <- rmse(4,0.1,F,F,F,F,0,T,0.05,500))
```

##Calculating 95% Confidence Intervals of Estimators

###NOTE: Set the seed before each individual simulation

```{r}
#Function to determine if CI contains 0.75 (95% CI coverage) 
ci95 <- function(data,m){
  yes <- 0
  for(i in 1:m){
    ul.ind <- data[1,i] + (1.96*data[2,i])
    ll.ind <- data[1,i] - (1.96*data[2,i])
    if(((ll.ind < 0.75 ) & (ul.ind > 0.75))){
      yes <- yes + 1
    } else yes <- yes
  }
  return(yes)
}

#Bootstrap function for crude estimator (Figures out estimator mean and std. error)
sim.boot.crude <- function(data, gamma, treat.prev, n){
  i <- sample(1:n, size=n, replace=TRUE)
  x.boot <- data[i,]
  ps <- ps.model(x.boot,gamma, treat.prev, n)
  z <- treat.assign(ps,n)
  y <- outcomeModel(x.boot,z,n)
  x.boot <- data.frame(x.boot, ps, z, y)
  crude <- (sum(x.boot[,8]*x.boot[,9])/sum(x.boot[,8])) - (sum((1-x.boot[,8])*x.boot[,9])/sum((1-x.boot[,8])))
  return(crude)
}

#Performing the bootstrap on crude estimator 
data.boot.crude <- function(gamma, treat.prev, n){
  x <- gen(n)
  crude.star <- replicate(100, expr = sim.boot.crude(x,gamma,treat.prev,n))
  return(c(mean(crude.star), std.error(crude.star)))
}

#Replicate the bootstraps and find 95% CI coverage
set.seed(1234)
crude.star <- replicate(100, expr = data.boot.crude(1,0.4,500), simplify=TRUE)
ci95(crude.star,100)
crude.star <- replicate(100, expr = data.boot.crude(2,0.4,500), simplify=TRUE)
ci95(crude.star,100)
crude.star <- replicate(100, expr = data.boot.crude(3,0.4,500), simplify=TRUE)
ci95(crude.star,100)
crude.star <- replicate(100, expr = data.boot.crude(4,0.4,500), simplify=TRUE)
ci95(crude.star,100)

#Bootstrap function for overlap estimator (Finds mean and std. error of overlap estimator of each dataset)
sim.boot.overlap <- function(data, gamma, treat.prev, n){
  i <- sample(1:n, size=n, replace=TRUE)
  x.boot <- data[i,]
  ps <- ps.model(x.boot,gamma, treat.prev, n)
  z <- treat.assign(ps,n)
  y <- outcomeModel(x.boot,z,n)
  x.boot <- data.frame(x.boot, ps, z, y)
  omega_ol <- omega.ol(x.boot,n)
  x.boot <- data.frame(x.boot,omega_ol)
  (overlap <- (sum(x.boot[,8]*x.boot[,9]*x.boot[,10])/sum(x.boot[,8]*x.boot[,10])) - 
  sum((1-x.boot[,8])*x.boot[,9]*x.boot[,10])/sum((1-x.boot[,8])*x.boot[,10]))
  return(overlap)
}

#Performing the bootstrap on overlap estimator
data.boot.overlap <- function(gamma, treat.prev, n){
  x <- gen(n)
  ov.star <- replicate(100, expr = sim.boot.overlap(x,gamma,treat.prev,n))
  return(c(mean(ov.star), std.error(ov.star)))
}

#Replicate the bootstraps and find 95% coverage
set.seed(1234)
overlap.star <- replicate(100, expr = data.boot.overlap(1,0.4,500), simplify=TRUE)
ci95(overlap.star,100)
overlap.star <- replicate(100, expr = data.boot.overlap(2,0.4,500), simplify=TRUE)
ci95(overlap.star,100)
overlap.star <- replicate(100, expr = data.boot.overlap(3,0.4,500), simplify=TRUE)
ci95(overlap.star,100)
overlap.star <- replicate(100, expr = data.boot.overlap(4,0.4,500), simplify=TRUE)
ci95(overlap.star,100)

#Bootstrap function for ipw estimator (Finds mean and std. error of ipw estimator of each dataset)
sim.boot.ipw <- function(data, gamma, treat.prev, n){
  i <- sample(1:n, size=n, replace=TRUE)
  x.boot <- data[i,]
  ps <- ps.model(x.boot,gamma, treat.prev, n)
  z <- treat.assign(ps,n)
  y <- outcomeModel(x.boot,z,n)
  x.boot <- data.frame(x.boot, ps, z, y)
  omega_ipw <- omega.ipw(x.boot,n)
  x.boot <- data.frame(x.boot,omega_ipw)
  ipw <- (sum(x.boot[,8]*x.boot[,9]*x.boot[,10])/sum(x.boot[,8]*x.boot[,10])) - 
  (sum((1-x.boot[,8])*x.boot[,9]*x.boot[,10])/sum((1-x.boot[,8])*x.boot[,10]))
  return(ipw)
}

#Performing the bootstrap on ipw estimator
data.boot.ipw <- function(gamma, treat.prev, n){
  x <- gen(n)
  ipw.star <- replicate(100, expr = sim.boot.ipw(x,gamma,treat.prev,n))
  return(c(mean(ipw.star), std.error(ipw.star)))
}

#Replicate the bootstraps and find 95% coverage
set.seed(1234)
ipw.star <- replicate(100, expr = data.boot.ipw(1,0.4,500), simplify=TRUE)
ci95(ipw.star,100)
ipw.star <- replicate(100, expr = data.boot.ipw(2,0.4,500), simplify=TRUE)
ci95(ipw.star,100)
ipw.star <- replicate(100, expr = data.boot.ipw(3,0.4,500), simplify=TRUE)
ci95(ipw.star,100)
ipw.star <- replicate(100, expr = data.boot.ipw(4,0.4,500), simplify=TRUE)
ci95(ipw.star,100)

#Bootstrap function for symmetrically trimmed ipw estimator (Finds mean and std. error of sym trim ipw estimator of each dataset)
sim.boot.ipw.strim <- function(data, gamma, treat.prev, alpha, n){
  i <- sample(1:n, size=n, replace=TRUE)
  x.boot <- data[i,]
  ps <- ps.model(x.boot,gamma, treat.prev, n)
  z <- treat.assign(ps,n)
  y <- outcomeModel(x.boot,z,n)
  x.boot <- data.frame(x.boot, ps, z, y)
  x.boot.trunc <- sym.trim(x.boot,alpha,n)
  n2 <- length(x.boot.trunc[,1])
  omega_ipw_trim <- omega.ipw.trim(x.boot.trunc,n2)
  x.boot.trunc <- data.frame(x.boot.trunc,omega_ipw_trim)
  ipw.trim <- (sum(x.boot.trunc[,8]*x.boot.trunc[,9]*x.boot.trunc[,10])/sum(x.boot.trunc[,8]*x.boot.trunc[,10])) - 
  (sum((1-x.boot.trunc[,8])*x.boot.trunc[,9]*x.boot.trunc[,10])/sum((1-x.boot.trunc[,8])*x.boot.trunc[,10]))
  return(ipw.trim)
}

#Performing the bootstrap on sym trim ipw estimator
data.boot.ipw.strim <- function(gamma, treat.prev, alpha, n){
  x <- gen(n)
  ipw.strim.star <- replicate(100, expr = sim.boot.ipw.strim(x,gamma,treat.prev,alpha,n))
  return(c(mean(ipw.strim.star), std.error(ipw.strim.star)))
}

#Replicate the bootstraps and find 95% coverage
set.seed(1234)
ipw.strim.star <- replicate(100, expr = data.boot.ipw.strim(1,0.4,0.15,500), simplify=TRUE)
ci95(ipw.strim.star,100)
ipw.strim.star <- replicate(100, expr = data.boot.ipw.strim(2,0.4,0.15,500), simplify=TRUE)
ci95(ipw.strim.star,100)
ipw.strim.star <- replicate(100, expr = data.boot.ipw.strim(3,0.4,0.15,500), simplify=TRUE)
ci95(ipw.strim.star,100)
ipw.strim.star <- replicate(100, expr = data.boot.ipw.strim(4,0.4,0.15,500), simplify=TRUE)
ci95(ipw.strim.star,100)
```


